Reply To Examiners

### 2014-05-05 answer_thesis_examiner/chap2.tex
auto

%The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
%I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
%They, and some other articles, have been included in the thesis.

@@

=====

Examiner No. 2 suggests to further emphasize the significance of the research motivation in \textbf{Section 1.1 and Section 1.2}.
In a similar fashion, the conclusion chapter should also include the research objectives.
These have been updated in the revised thesis.
Even though I would wish to note that the research objectives have been spelled out in the Introduction chapter.
The examiner also suggested to change the word ``theory'' to ``model''.
That has also been applied through out the thesis.

\textbf{The second main comment} is to further highlight the novelty claim, which can be splitted into two parts.

\textit{In the first part}, the examiner appears to discount the novelty claim by suggesting that:
 ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
The main approach, in actuality, differs in a subtle but important way:
The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
These results are well known to be applicable to POLSAR.
Thus, the derived models by nature are multi-dimensional model.
However, when collapsed into single-dimension, they match perfectly with existing SAR models.
As such, the proposed models can be considered as an extension of existing statistical models for SAR.

\textit{In the second part}, the Examiner expresses his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria''.
His main concern: ``the proposed log-transform model will introduce an inevitable bias error''.
It is no doubt tricky to evaluate evaluation criteria.
And I can empathize with his feelings.
Still, I wish to point out that MSE evaluation inherently includes bias evaluation. 
In fact it has two components: 1. bias evaluation and 2. variance evaluation, which for SAR speckle filter evaluation translates into 1. radiometric preservation and 2. noise suppression respectively.

@@

\textbf{To conclude}, I appreciate the fact that the Examiner is able to a summarize the long thesis into a single sentence.
Also, portions of this thesis has been extracted out as scientific articles and submitted for peer review.
Various errata exposed by Examiner No. 2 and have also been updated in the thesis.
Last but not least, I wish to express my appreciation towards Examiner No.2 for his careful and detailed review.

>>>>

\replyToComment
    {The work done has great potential to be published in high impact factor journals such as JSTAR, IJRS and PIER}
    {I appreciate the Examiner's vote of confidence. Portions of the thesis has been extracted out as academic papers and submitted for peer-review.}

@@

%=====
%
%Examiner No. 2 suggests to further emphasize the significance of the research motivation in \textbf{Section 1.1 and Section 1.2}.
%In a similar fashion, the conclusion chapter should also include the research objectives.
%These have been updated in the revised thesis.
%Even though I would wish to note that the research objectives have been spelled out in the Introduction chapter.
%The examiner also suggested to change the word ``theory'' to ``model''.
%That has also been applied through out the thesis.
%
%\textbf{The second main comment} is to further highlight the novelty claim, which can be splitted into two parts.
%
%\textit{In the first part}, the examiner appears to discount the novelty claim by suggesting that:
% ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
%The main approach, in actuality, differs in a subtle but important way:
%The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
%These results are well known to be applicable to POLSAR.
%Thus, the derived models by nature are multi-dimensional model.
%However, when collapsed into single-dimension, they match perfectly with existing SAR models.
%As such, the proposed models can be considered as an extension of existing statistical models for SAR.
%
%\textit{In the second part}, the Examiner expresses his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria''.
%His main concern: ``the proposed log-transform model will introduce an inevitable bias error''.
%It is no doubt tricky to evaluate evaluation criteria.
%And I can empathize with his feelings.
%Still, I wish to point out that MSE evaluation inherently includes bias evaluation. 
%In fact it has two components: 1. bias evaluation and 2. variance evaluation, which for SAR speckle filter evaluation translates into 1. radiometric preservation and 2. noise suppression respectively.

@@

%\textbf{To conclude}, I appreciate the fact that the Examiner is able to a summarize the long thesis into a single sentence.
%Also, portions of this thesis has been extracted out as scientific articles and submitted for peer review.
%Various errata exposed by Examiner No. 2 and have also been updated in the thesis.
%Last but not least, I wish to express my appreciation towards Examiner No.2 for his careful and detailed review.
